Experiments on ANTS Algorithms Without Communication

### 2014-12-08 paper/draft.tex
starting final draft and some data

The lines algorithm is the study of \cite{lenzen2014trade}, where they cover a lines algorithm which is non-uniform in $D$ and non-uniform in $k$. We use the ideas of \cite{feinerman2012collaborative} to design a lines algorithm which is uniform in both $k$ and $D$.

>>>>

The lines algorithm is the study of \cite{lenzen2014trade}, where they cover a lines algorithm which is non-uniform in $D$ and non-uniform in $k$. We use the ideas of \cite{feinerman2012collaborative} to design a lines algorithm which is uniform in both $k$ and $D$. The lines algorithm has many optimizations since \cite{lenzen2014trade} are trying to reduce \emph{selection complexity}. Selection complexity is a metric which measures how likely an algorithm is to occur naturally in nature. Of course, this notion is very vague, but formally, the selection complexity $\chi$ of an algorithm $A$ is $\chi(A) = b + \log l$ where $b$ is the amount of memory usage and $l$ is smallest $l$ for which the algorithm does not need finer probabilities than $2^{-l}$. In \cite{lenzen2014trade}, Lenzen et al. provided a lines algorithm with selection complexity $O(\log \log D)$.

\subsubsection{Non-uniform in $D$} First, we will explain the simple lines algorithm which is non-uniform in $D$. Remember, $D$ is an upper bound on the distance the treasure. The lines algorithm is very simple to explain. With probability $\frac{1}{2}$, an agent moves up, otherwise, it moves down. Then it continues moving in that direction until a coin with head probability $\frac{D-1}{D}$ lands on tails. It repeats the process for the left and right directions. The pseudocode is shown, $C_p$ will denote a coin which lands heads with probability $p$, and so $C_p$ will return a 0 or 1, with 0 denoting heads.

The algorithm relies on it novel way of walking in lines by approximately counting. The following procedure shows how an agent would move in a particular direction.

\begin{codebox}
\Procname{moveDirection(dir)}
\li \While $C_{\frac{D-1}{D}} = 0$ \Then
\li agent moves in direction dir \End
\end{codebox}

Note that the above algorithm, while it uses contant memory, it does need to sample from a distribution with probability as fine as $\frac{1}{D}$. This is fine, since in this case, $l = \log D$. 
Now that we know how agents move in a particular direction, they randomly pick a direction to travel.

\begin{codebox}
\Procname{Each agent performs the following iteration}
\li dir[0] $\leftarrow$ up, dir[1] $\leftarrow$ down
\li $i \leftarrow C_{\frac{1}{2}}$
\li moveDirection($i$)
\li \If $C_{\frac{1}{2}} = 0$ \Then
\li moveDirection(left)
\li \Else moveDirection(right) \End \End
\li return to origin
\end{codebox}

The one thing to note is that the last line, ``return to origin" would need to keep the location of the ant. This would require $\log D$ memory, which we cannot afford; however, it is an assumption in the model that agents can return to the origin.

% TO DO
The sketch of the proof of correctness is the following ...????

\subsubsection{Uniform in $D$}
